s.function

### 2023-04-06 src/la_ranks_n1.Rmd
various outputs

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only05.png")

@@

  mutate(alpha = ifelse(abs(diff_1st) < 3.75, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

>>>>

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only95.png")

@@

  mutate(alpha = ifelse(abs(diff_1st) > 199.5, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

### 2023-04-06 src/level_lisa_oa.Rmd
various outputs

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)

@@

Website density regressions to London

@@

Website density regressions to the nearest city

@@

Website density regressions to the nearest retail centre

>>>>

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
library(plm)
library(lmtest)

@@

## Panel regressions

```{r}
# London
model <- plm(log(n+0.001) ~ log(London+.001)*as.factor(year), 
             data = df,
             index = c("oa11cd", "year"),
             model = "within",
             effect = "twoways")
summary(model)

est <- coeftest(model, vcov = vcovHC, type = "HC1") # same
int <- confint(est)

out.model <- bind_cols(tidy(est), 
                       as_tibble(int)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(year = 1997:2012) %>% 
  rename(conf.low = '2.5 %',
         conf.high = '97.5 %')

path.out <- paste0(path,"/outputs/lisa/b_panel_dist_london_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                    width = 0.2,size  = 1,
                    position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("Interaction coefficients: distance*year, robust st. errors") + xlab("") + 
  ggtitle("Regression coefficients: distance to London on website counts, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

# Cities
model <- plm(log(n+0.001) ~ log(dist+.001)*as.factor(year), 
             data = df,
             index = c("oa11cd", "year"),
             model = "within",
             effect = "twoways")
summary(model)

est <- coeftest(model, vcov = vcovHC, type = "HC1") # same
int <- confint(est)

out.model <- bind_cols(tidy(est), 
                       as_tibble(int)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(year = 1997:2012) %>% 
  rename(conf.low = '2.5 %',
         conf.high = '97.5 %')

path.out <- paste0(path,"/outputs/lisa/b_panel_dist_cities_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                    width = 0.2,size  = 1,
                    position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("Interaction coefficienst: distance*year, robust st. errors") + xlab("") + 
  ggtitle("Regression coefficients: distance to Cities on website counts, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

# Retail centres
model <- plm(log(n+0.001) ~ log(dist.retail+.001)*as.factor(year), 
             data = df,
             index = c("oa11cd", "year"),
             model = "within",
             effect = "twoways")
summary(model)

est <- coeftest(model, vcov = vcovHC, type = "HC1") # same
int <- confint(est)

out.model <- bind_cols(tidy(est), 
                       as_tibble(int)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(year = 1997:2012) %>% 
  rename(conf.low = '2.5 %',
         conf.high = '97.5 %')

path.out <- paste0(path,"/outputs/lisa/b_panel_dist_retail_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                    width = 0.2,size  = 1,
                    position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("Interaction coefficients: distance*year, robust st. errors") + xlab("") + 
  ggtitle("Regression coefficients: distance to Retail Centres on website counts, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)
```

## Website density regressions to London, cross-section

@@

## Website density regressions to the nearest city, cross-section

@@

## Website density regressions to the nearest retail centre, cross-section

### 2023-04-06 src/s_la_per_firm.Rmd
various outputs

library(tidyverse)
library(broom)
library(rprojroot)
library(rgdal)
library(sf)
library(modelr)
library(survival)

@@

>>>>

library(tidyverse)
library(broom)
library(rprojroot)
library(rgdal)
library(sf)
library(modelr)
library(survival)
library(rgeos)
library(spdep)
library(rgdal)
library(tidygeocoder)
library(geosphere)
library(raster)
library(rms)
library(stargazer)

@@

## Explain fast/slow

### load data

```{r}
a.la <- read_csv(path.out)

library(readxl)
library(httr)
url.classes <- "https://www.ons.gov.uk/file?uri=/methodology/geography/geographicalproducts/areaclassifications/2011areaclassifications/datasets/clustermembershipv2.xls"

GET(url.classes, write_disk(tf <- tempfile(fileext = ".xls", tmpdir = paste0(path, "/data/temp"))))

classes.la <- read_excel(tf, sheet = 3, range = "A10:I399") %>% 
  rename(ladcd = Code,
         supergroup = 'Supergroup Code',
         group = 'Group Code',
         subgroup = 'Subgroup Code')

a.la <- a.la %>% left_join(classes.la) %>% 
  mutate(fast.binary = if_else(fast == "fast", 1, 0))
sapply(a.la, function(x) sum(is.na(x))) # 16 mising

### Distances

First set up the destinations. Origins are all the LA.

Major cities from [source](https://www.citypopulation.de/en/uk/cities/).
Retail centres from [source](https://data.cdrc.ac.uk/dataset/retail-centre-boundaries)

```{r}
# LA centroids
la.c <- gCentroid(la, byid=TRUE)@coords %>% 
  as.data.frame() %>%
  bind_cols(la@data) %>% 
  dplyr::select(LAD21CD, x, y) %>% 
  remove_rownames()

# cities
city.names <- c("London, UK", 
"Birmingham, UK",
"Glasgow, UK",
"Liverpool, UK",
"Bristol, UK",
"Manchester, UK",
"Sheffield, UK",
"Leeds, UK",
"Edinburgh, UK",
"Leicester, UK")

cities <- geo(city.names, no_query = F, method = "arcgis")

# retail centres
geo.path <- paste0(path, "/data/raw/Retail_Boundaries_UK.gpkg")
retail <-readOGR(geo.path) 
#retail.major.cetres <- subset(retail, retail$Classification == "Major Town Centre") #%>% 
retail.major.cetres.help <- gCentroid(retail, byid=TRUE)@coords %>% 
  as.data.frame() %>% 
  add_rownames(var = "id") #%>%

retail.major.cetres <- retail.major.cetres.help %>% 
  st_as_sf(coords = c("x", "y"), crs = 27700) %>%
  st_transform(4326) %>%
  st_coordinates() %>%
  as_tibble() %>% 
  bind_cols(retail.major.cetres.help$id) %>% 
  rename(id = '...3') %>% 
  left_join(retail@data %>% mutate(id = rownames(retail@data)), by = 'id')
```

Distance to cities

```{r}
dist <- distm(cbind(la.c$x, la.c$y), cbind(cities$long, cities$lat), fun=distHaversine) 
dist <- round((dist/1000),2) %>% 
  as_tibble()

city.names <- city.names %>% stringr::str_remove(", UK")
names(dist) <- city.names

dist <- dist %>% bind_cols(la.c$LAD21CD) %>% 
  rename(ladcd = last_col()) %>% 
  relocate(ladcd)

# dist$dist <- names(dist)[apply(dist[-1], MARGIN = 1, FUN = which.min)]
# dist$distMet <- apply(dist[,2:11], 1, min)

dist <- transform(dist, dist = do.call(pmin, dist[-1]))

# NOT USED AS IT SCREWS UP THE REGRESSIONS
# Complete panel, N = 3871903, 17 year * 227759 OA
# df <- df %>% bind_rows(dist %>% select(oa11cd)) %>% 
#   mutate(year = ifelse(is.na(year),1000, year),
#          country = substring(oa11cd, 1, 1)) %>% 
#   filter(country != "L" & country != "M" & country != "N") %>% 
#   filter(!is.na(country)) %>% 
#   complete(year, oa11cd, fill = list(n = 0)) %>% 
#   filter(year!=1000,
#          !is.na(oa11cd)) %>% 
#   select(-country)

# tests
# test$country <- substring(test$oa11cd, 1, 1)
# unique(test$country)
# length(unique(test$oa11cd))

# calculate area
la$SHAPE_Area <- area(la) #/ 1000000

# Join with distance and area
a.la <- a.la %>% left_join(dist, by = c("ladcd" = "ladcd")) 
sapply(a.la, function(x) sum(is.na(x)))
```

Distance to retail centres

```{r}
dist.retail <- distm(cbind(la.c$x, la.c$y), cbind(retail.major.cetres$X, retail.major.cetres$Y), fun=distHaversine) 
dist.retail <- round((dist.retail/1000),2) %>% 
  as_tibble()

# retail.names <- retail.major.cetres$RC_Name
# names(dist.retail) <- retail.names

dist.retail <- dist.retail %>% bind_cols(la.c$LAD21CD) %>% 
  rename(LAD21CD = last_col()) %>% 
  relocate(LAD21CD)

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% dplyr::select(LAD21CD, dist.retail)

# Join with complete panel
a.la <- a.la %>% left_join(dist.retail, by = c("ladcd" = "LAD21CD"))

sapply(a.la, function(x) sum(is.na(x)))
```

### Regressions

**TODO** add distance, see what classes mean, try lm

model <- glm(fast.binary ~ log(London + 0.001) + log(dist + 0.001) + log(dist.retail + 0.001) + as.factor(subgroup), family=binomial (link='logit'), data = a.la)
summary(model)
stargazer(model, type = 'text')
```

For Nagelkerke R2

```{r}
model2 <- lrm(fast.binary ~ log(London + 0.001) + log(dist + 0.001) + log(dist.retail + 0.001) + subgroup, data = a.la)
print(model2)
```

### 2023-04-06 src/s_oa.Rmd
various outputs

library(tidyverse)
library(broom)
library(rprojroot)

@@

@@

```{r}
# a <- as_tibble()
# all.oa <- unique(df$oa11cd)
# #for (oa in all.oa){
# a <- foreach(oa = all.oa, .combine = 'rbind',
#              #.final =  function(x) setNames(x, names(all.oa)),
#           .packages = c("tidyverse",
#                                     "broom")) %dopar% {
#   data <- df %>% filter(oa11cd==oa) %>%
#     dplyr::select(year, oa11cd, n) 
#     #lm(n~year, data = .)
#     #tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = .)), , error=function(e) NULL)
#   tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)
#   #tryCatch(a <-rbind(a,b), error=function(e) NULL)
# }

@@

a <- foreach(oa = all.oa, .combine = 'rbind', .packages = c("tidyverse",
                           "broom")) %dopar% 
  {
    data <- df %>% filter(oa11cd==oa) %>%
    dplyr::select(year, oa11cd, n) 
    tryCatch(model <- tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)

@@

    c(oa, model)
    }

@@

a <- a %>% filter(term=="xmid") %>% 
    bind_cols(all.oa) %>% 
    mutate(estimate = round(estimate, 0)) %>% 
    filter(p.value < 0.01) %>%    # (227759 - 212782)/227759  # 6% not sig 
    rename(id = ...6) %>% 
    select(id, estimate)
```

@@

>>>>

library(tidyverse)
library(broom)
library(rprojroot)
library(tidyverse)
library(broom)
library(rprojroot)
library(rgdal)
library(sf)
library(modelr)
library(rgeos)
library(spdep)
library(rgdal)
library(tidygeocoder)
library(geosphere)
library(raster)
library(Matrix)
library(rms)
library(stargazer)
library(doParallel)
library(foreach)
library(maptools)
#library(survival)

@@

## Spatial data

# get GB
path.gb <- "/hdd/internet_archive/archive/gis/Countries_December_2014_Full_Clipped_Boundaries_in_Great_Britain.shp"
gb <- readOGR(path.gb)
# spatial transformations
gb <- spTransform(gb, CRS("+init=epsg:4326"))
```

@@

```{r}
a <- as_tibble()
all.oa <- unique(df$oa11cd)
# #for (oa in all.oa){
# a <- foreach(oa = all.oa, .combine = 'rbind',
#              #.final =  function(x) setNames(x, names(all.oa)),
#           .packages = c("tidyverse",
#                                     "broom")) %dopar% {
#   data <- df %>% filter(oa11cd==oa) %>%
#     dplyr::select(year, oa11cd, n) 
#     #lm(n~year, data = .)
#     #tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = .)), , error=function(e) NULL)
#   tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)
#   #tryCatch(a <-rbind(a,b), error=function(e) NULL)
# }

# test for a single OA
help <- df %>% dplyr::filter(oa11cd == "E00000706")
model <- tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = help))
model %>% as.data.frame() %>% 
  filter(term=="xmid") %>% 
    #bind_cols(all.oa) %>% 
    mutate(estimate = round(estimate, 0)) %>% 
    filter(p.value < 0.01) %>%    # (227759 - 212782)/227759  # 6% not sig 
    rename(id = ...6) %>% 
    dplyr::select(id, estimate)

@@

a <- foreach(oa = all.oa, .combine = 'rbind', .packages = c("tidyverse", #
                           "broom")) %dopar% 
  {
    data <- df %>% filter(oa11cd==oa) %>%
      dplyr::select(year, oa11cd, n) 
    tryCatch(model <- tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)

@@

    #tryCatch(c(oa, model), error=function(e) NULL) #
    #tryCatch(model$oa <-  oa, error=function(e) NULL) #
    tryCatch(model %>% mutate(id = oa), error=function(e) NULL)
    }

@@

a <- a %>% filter(term=="xmid") %>% 
    #mutate(estimate = round(estimate, 2)) %>% 
    filter(p.value < 0.01) %>%    # (227759 - 212782)/227759  # 6% not sig 
    dplyr::select(id, estimate)
```

@@

## Explain fast/slow

### load data

Source: https://www.ons.gov.uk/methodology/geography/geographicalproducts/areaclassifications/2011areaclassifications/datasets

```{r}
a <- read_csv(path.out)

library(readxl)
library(httr)
url.classes <- "https://www.ons.gov.uk/file?uri=/methodology/geography/geographicalproducts/areaclassifications/2011areaclassifications/datasets/2011oacclustersandnamesexcelv2.zips"

path.in <- paste0(path, "/data/raw/2011 OAC Clusters and Names Excel v2.xlsx")
classes.oa <- read_excel(path.in, sheet = 2) %>% 
  rename(id = 'Output Area Code',
         supergroup = 'Supergroup Code',
         group = 'Group Code',
         subgroup = 'Subgroup Code')

a <- a %>% left_join(classes.oa) %>% 
  mutate(fast.binary = if_else(estimate < 2002.926, 1, 0))
sapply(a, function(x) sum(is.na(x))) # 16 mising
```

### Distances

# NOT USED AS IT SCREWS UP THE REGRESSIONS
# Complete panel, N = 3871903, 17 year * 227759 OA
# df <- df %>% bind_rows(dist %>% dplyr::select(oa11cd)) %>%
#   mutate(year = ifelse(is.na(year),1000, year),
#          country = substring(oa11cd, 1, 1)) %>%
#   filter(country != "L" & country != "M" & country != "N") %>%
#   filter(!is.na(country)) %>%
#   complete(year, oa11cd, fill = list(n = 0)) %>%
#   filter(year!=1000,
#          !is.na(oa11cd)) %>%
#   dplyr::select(-country)

# calculate area
oa.gb$area <- area(oa.gb) #/ 1000000

# Join with distance and area
a <- a %>% left_join(dist, by = c("id" = "oa11cd")) %>% 
  left_join(oa.gb@data, by = c("id" = "id")) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)
sapply(a, function(x) sum(is.na(x))) # mising NI

# Join with complete panel
a <- a %>% left_join(dist.retail, by = c("id" = "oa11cd"))

sapply(a, function(x) sum(is.na(x)))
```

### Regressions

```{r}
model <- glm(fast.binary ~ log(London + 0.001) + log(dist + 0.001) + log(dist.retail + 0.001) + as.factor(subgroup), family=binomial (link='logit'), data = a)
summary(model)
stargazer(model, type = 'text')
```

For Nagelkerke R2

```{r}
model2 <- lrm(fast.binary ~ log(London + 0.001) + log(dist + 0.001) + log(dist.retail + 0.001) + group, data = a)
print(model2)
```
